\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-11-24 papers/jss/article.Rnw
Remove a duplicate word in the last paragraph of the introduction, add a word to fix a linewrap in section 4, and add a paragraph to the beginning of section 7 to make it more interesting.  More work on sections 6,7, and 8 is sorely needed.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@903 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

This paper describes an \proglang{R} interface to Protocol Buffers,
and is organized as follows. Section~\ref{sec:protobuf}
provides a general high-level overview of Protocol Buffers as well as a basic
motivation for their use.
Section~\ref{sec:rprotobuf-basic} describes the interactive \proglang{R} interface
provided by the \pkg{RProtoBuf} package, and introduces the two main abstractions:
\emph{Messages} and \emph{Descriptors}.  Section~\ref{sec:rprotobuf-classes}
details the implementation details of the main S4 classes and methods.  
Section~\ref{sec:types} describes the challenges of type coercion
between \proglang{R} and other languages.  Section~\ref{sec:evaluation} introduces a
general \proglang{R} language schema for serializing arbitrary \proglang{R} objects and evaluates
it against the serialization capabilities built directly into \proglang{R}.  Sections~\ref{sec:mapreduce}
and \ref{sec:opencpu} provide real-world use cases of \pkg{RProtoBuf}
in MapReduce and web service environments, respectively, before
Section~\ref{sec:summary} concludes.

@@

The \code{EnumDescriptor} contains information about what values a
type defines, while the \code{EnumValueDescriptor} describes an
individual enum constant of a particular type.  The \verb|$| operator
can be used to retrieve the value of enum constants contained in the
EnumDescriptor, or to invoke methods.

@@

>>>>

This paper describes an \proglang{R} interface to Protocol Buffers,
and is organized as follows. Section~\ref{sec:protobuf}
provides a general high-level overview of Protocol Buffers as well as a basic
motivation for their use.
Section~\ref{sec:rprotobuf-basic} describes the interactive \proglang{R} interface
provided by the \pkg{RProtoBuf} package, and introduces the two main abstractions:
\emph{Messages} and \emph{Descriptors}.  Section~\ref{sec:rprotobuf-classes}
details the implementation of the main S4 classes and methods.  
Section~\ref{sec:types} describes the challenges of type coercion
between \proglang{R} and other languages.  Section~\ref{sec:evaluation} introduces a
general \proglang{R} language schema for serializing arbitrary \proglang{R} objects and evaluates
it against the serialization capabilities built directly into \proglang{R}.  Sections~\ref{sec:mapreduce}
and \ref{sec:opencpu} provide real-world use cases of \pkg{RProtoBuf}
in MapReduce and web service environments, respectively, before
Section~\ref{sec:summary} concludes.

@@

The \code{EnumDescriptor} type contains information about what values a
type defines, while the \code{EnumValueDescriptor} describes an
individual enum constant of a particular type.  The \verb|$| operator
can be used to retrieve the value of enum constants contained in the
EnumDescriptor, or to invoke methods.

@@

Protocol Buffers have been used extensively at Google for almost all
RPC protocols, and for storing structured information in a variety of
persistent storage systems since 2000 \citep{dean2009designs}.  The
\pkg{RProtoBuf} package has been in widespread use by hundreds of
analysts at Google since 2010.
